Impact: An Indirect Dependency Awareness Tool For Software Development

### 2012-12-18 icse-chase-2013/paper.tex
First rough now has images.

\subsection{Design}
Compared to tool design for direct conflicts, the major concern of 
indirect conflict tools is to relate technical objects to one another
with a "uses" mentality. To say that object 1 uses object 2 is to infer
a technical relationship between the two objects which can be used
in part to detect indirect conflict that arise from modifying object
2. This kind of relationship is modeled after a directed graph. Each
technical object and represented by node while each "uses"
relationship is represented by a directed edge. This representation
is used to indicate all indirect relationships within a software project.\\

@@

@@

Now that the indirect conflicts have been found, we use the
ownership information of our technical objects to send alerts to
those developers involved in the indirect conflict. All owners
of methods which invoke those that have been changed are alerted
to the newly changed method. This can been seen in
Figure~\ref{}, the user interface of Impact. Here, in an RSS type
feed, the changing developer, time of change, changed method,
invoking methods, and commit message are all displayed. This 
list is auto updating as new commits are push to the central
git repository. Developers are now free to use this information
to be aware of and solve indirect conflicts which arise at the
method level.\\

>>>>

\subsection{Design}
Compared to tool design for direct conflicts, the major concern of 
indirect conflict tools is to relate technical objects to one another
with a "uses" mentality. To say that object 1 uses object 2 is to infer
a technical relationship between the two objects which can be used
in part to detect indirect conflict that arise from modifying object
2. This kind of relationship is modelled after a directed graph. Each
technical object and represented by node while each "uses"
relationship is represented by a directed edge. This representation
is used to indicate all indirect relationships within a software project.\\

@@

\begin{figure}[t!]
\includegraphics{images/CallGraph}
\caption{Technical object directed graph with ownership\label{fig:graph}}
\end{figure}

@@

Now that the indirect conflicts have been found, we use the
ownership information of our technical objects to send alerts to
those developers involved in the indirect conflict. All owners
of methods which invoke those that have been changed are alerted
to the newly changed method. This can been seen in
Figure~\ref{fig:impact}, the user interface of Impact. Here, in an RSS type
feed, the changing developer, time of change, changed method,
invoking methods, and commit message are all displayed. This 
list is auto updating as new commits are push to the central
git repository. Developers are now free to use this information
to be aware of and solve indirect conflicts which arise at the
method level.\\

\begin{figure}[t!]
\includegraphics{images/ImpactDemo}
\caption{Impact's RSS type information feed.\label{fig:impact}}
\end{figure}
